Hemodynamic responses of the Parahippocampal Place Area to spatial cues in a movie and it's audio-description

### 2020-04-29 paper/main.tex
add some notes to discussion
revise manuscript (& references) after feedback

% Präteritum oder Präsens? Ist momentan gemischt; find's ok so.
% N=14 is inner join of AV & AO
\todo[inline]{The next paragraphs contain a bunch of methods already; reduce this to talk about the general approach:
    a) annotation of events,
    b) investigation of model quality,
    c) cross-analysis of datasets.
    d) Possibly cite https://psyarxiv.com/sdbqv/
    and declare that this study is a concrete realization of that promise
}
In this study, we analyze data of three publicly available datasets from the same set of 14 participants as part of the studyforrest data set (\href{http://www.studyforrest.org}{studyforrest.org}).
We exploratorily investigate how the parahippocampal gyrus [or more general ``human brain''?] responds to ``spatially relevant'' events embedded in a 2h audio-visual movie \citep{hanke2016simultaneous} and its audio-description of the same length \citep{hanke2014audiomovie}.
We compare these results to PPA localizations that were obtained from a dedicated visual localizer experiment \citep{sengupta2016extension}.
Both natural stimuli were originally designed to entertain an audience and to capture attention free from any perceptual or behavioral task.
We annotated events in the otherwise unknown temporal structure of both stimuli.
In/for the movie, we annotated different kinds of cinematographic cuts \citep{haeusler2016annotation} as presumably ``spatially relevant'' events.
Our rationale was that cuts re-orient the viewer in the depicted environment independent from the exact visual content in the movie frame following the cut.
In/for the audio-description, we annotated verbal clues about the missing visual content given by the audio-description's additional narrator [citep{haeusler2020speechanno}].
In conformity to the analyses performed in the studies using not-naturalistic stimuli, we employed a standard multi-level, voxel-wise general linear model (GLM) % in order to???
% Practical reasons = Es war viel einfacher nouns der audio-description als Frameinhalt des Films zu annotieren
For practical reasons, and encouraged by \citep{aziz2008modulation} and \citep{aminoff2013role}, we focus on the audio-description as a possible life-like stimulus free from any task to localize a ``visual area'' in individual study participants.

\section{Methods}
\todo[inline]{Specific data outputs should be explicitly referenced via data citation (see Data Records and Data Citations, below)}
\todo[inline]{MIH: we should consider making a statement how often these datasets have been analyzed be independent groups already -> Frage: ist die Liste auf psychoinformatics.de ist aktuell/erschöpfend? Ist dann schnell eingebaut}
\todo[inline]{entsprechend der neuen Infos hier, oben das Ende der Einleitung kürzen}
We used data from three publicly available datsets as part of the studyforrest dataset (\href{http://www.studyforrest.org}{studyforrest.org}) that has already been used by other research groups for independent research questions before. We used fMRI data from 14 subjects who took part in three different studies. Namely the same subjects were
a) listening to the audio-description (AO study) \citep{hanke2014audiomovie}) of the movie ``Forrest Gump'', a dataset already used by [XY].
b) watching the actual audio-visual movie (AV study) \citep{hanke2016simultaneous}, a dataset already used by [XY].
c) participating in a dedicated block-wise visual localizer (LOC study) \citep{sengupta2016extension}, a dataset aready used by [XY]. An exhaustive description of the participants, stimulus creation, procedure, stimulation setup, and fMRI acquisition can be found in the corresponding publications  \citep{hanke2014audiomovie, hanke2016simultaneous, sengupta2016extension}. Following is a brief summary of most important aspects.
% Fokus auf die Naturalistic Stimuli; LOC study ist effektiv nicht mit drin

@@

\subsection{Stimulus Annotation}
\todo[inline]{einleitendes Blabla zu haeusler2020speechanno}
\todo[inline]{allg. überarbeiten; deutlich machen, WARUM WAS WIE annotiert wurde}
% Florian hat 2 Regeln falsch verstanden, sonst war übereinstimmung 90-95%
% Kategorie ``++'' enthält ausnahmesweise auch adverbiale Best. der Zeit.
% ggf. angeben, dass die effektiv identisch waren
\todo[inline]{aus Speech-Anno Paper 'descriptive-statistics-anno.py' übernehmen \& anpassen, um Statistiken und runcommand-file zu erstellen}
A further annotation of the audio-description's narrator was done manually: Two
persons performed a categorization of nouns embedded in sentences spoken by the
narrator to describe the movie's missing visual content.
Categories focus on the cinematographic scene's environment, inherent objects, persons, and a person's appearance.
A categorizing of nouns that serve as auditory cues about the movie's visual content. Comprised categories focus on the cinematographic scene's environment (geo, geo-room; setting\_new, setting\_old), inherent persons (female, female name; male, male name, person), their appearance (face, head; body, bodypart), and objects (object, furniture).
A preliminary annotation according to the rules [entweder im laufenden Text oder in Tabelle], einer neuen Tabelle oder im laufenden Text was done by one person and corrected in several runs by the author.

@@

\subsection{Statistical analysis}
A standard two-level general linear model (GLM) analysis was conducted in FEAT to create subject-specific results ($Z$-maps). A subsequent, third-level analysis averaged contrast estimates over subjects.

\subsubsection{first-level}
\paragraph{Regressors \todo{stimulus/statistical model?}}
To build the regressors for the GLMs, we took advantage of two publicly available annotations of the stimuli's temporal structure.
One annotation of speech occurring in the audio-description and movie [haeusler2020speechanno], and a second annotation of movie cuts and depicted locations \href{https://f1000research.com/articles/5-2273}{haeusler2016annotation}.
As a first step, the annotations were split via (\href{"https://github.com/chrhaeusler/studyforrest-data-annotations/blob/master/code/researchcut2segments.py"}{python script} into eight parts corresponding to the eight segments used in the scanner.
% wenn ich folgend den "null regressor" nehme, darf ich den ganzen Run - glaube ich - in der 2nd level Analyse gar nicht benutzen??
For the auditory stimulus, we used nouns embedded in sentences spoken by the narrator. The nouns are categorized by the clue they provide about a cinematographic scene's environment \todo{maybe skip the names and just cite the table} (geo, geo-room; setting\_new, setting\_rec), its inherent persons (female, female name; male, male name, person), a person's appearance (face, head; body, bodypart), and a scene's inherent objects (object, furniture).
% nope, kommt jetzt hier
Details on procedure to annotate the stimuli on a single-world level and details on the rules to manually categorize the nouns can be found in the \href{"https://www.overleaf.com/project/5d4ab1b759001b5db6ea2bc3"}{corresponding paper}.
We created 11 regressors from the XY (selected?) original categories by joining / merging some categories (female, females, fname; male, males, mname; face, head) into one regressor (sex\_f; sex\_m; fahead).
% over length of each noun
The regressors were modeled as boxcar functions at the end of each noun with a duration of 200 ms.
If a segment did not contain a single event for a specific regressor, a null regressor was chosen for that segment.
Five regressors related to the cinematographic cuts (s. below) were added to built contrasts of cross-modal negative control.
Two regressors reflecting auditory (low-level) features (left-right loudness volume / amplitude??? difference; root mean squared amplitude) aligned to the frame rate of (40\,ms) were modeled to reduce nuisance effects.
An overview and short explanation of the 11 regressors and 5 + 2 additional nuisance regressors can be found in Table xy.
% entgegen der Masterarbeit kommen hier für den Film keine Abbildungen zur Verdeutlichung, weniger Text; no cut erkläre ich nicht lang & breit
% die regressoren settinge_new & setting_old aus dem Hörspiel habe ich meiner meinung nach unnötigerweise im Film mit-modelliert; lasse mich da aber auch umstimmen
% -> noch mal reingucken; kamen im Grunde nur "auditorische Areale" als Cluster vor; umgekehrt gab's bei der visuellen Regressoren im Hörbuch keine sign. Cluster
For the audio-visual stimulus, we categorized the depicted location in the frame following one of the 869 cuts in the movie to built five regressors: 1) unfamiliar setting (US), 2) familiar setting (FS), 3) locale switch (LS), 4) unfamiliar perspective (UP), 5) familiar perspective (FP).
In order to build negative control contrasts, a sixth regressors was created by pseudo-randomly choosing frames present within a shot and apart from a cut. Regressors were modeled as boxcar function lasting 200\,ms after a cut.
An overview and short explanation of the six regressors and the additional nuisance regressors reflecting (auditory and) visual low-level features can be found in Table xy.
For both stimuli, regressors were convolved with a double gamma canonical hemodynamic response function (HRF).
Their temporal derivatives were added to compensate for small timing differences \citep{friston1998event}.
Six motion parameters were used as additional nuisance regressors. Finally, designs were filtered with the same high-pass filter (cutoff period of 150\,s) as the BOLD time series.

@@

\section{Discussion (movie)}
\begin{itemize}
\item lore ipsum
\end{itemize}

>>>>

% Präteritum oder Präsens? Ist momentan gemischt; find's ok so.
% N=14 is inner join of AV & AO
\todo[inline]{The next paragraphs contain a bunch of methods already; reduce this to talk about the general approach:
    a) annotation of events,
    b) investigation of model quality,
    c) cross-analysis of datasets.
    d) Possibly cite https://psyarxiv.com/sdbqv/
    and declare that this study is a concrete realization of that promise
}
In this study, we analyze data of three publicly available datasets from the same set of 14 participants as part of the studyforrest data set (\href{http://www.studyforrest.org}{studyforrest.org}).
We exploratorily investigate how the parahippocampal gyrus [or more general ``human brain''?] responds to ``spatially relevant'' events embedded in a 2h audio-visual movie \citep{hanke2016simultaneous} and its audio-description of the same length \citep{hanke2014audiomovie}.
We compare these results to PPA localizations that were obtained from a dedicated visual localizer experiment \citep{sengupta2016extension}.
Both natural stimuli were originally designed to entertain an audience and to capture attention free from any perceptual or behavioral task.
We annotated events in the otherwise unknown temporal structure of both stimuli.
In/for the movie, we annotated different kinds of cinematographic cuts \citep{haeusler2016cutanno} as presumably ``spatially relevant'' events.
Our rationale was that cuts re-orient the viewer in the depicted environment independent from the exact visual content in the movie frame following the cut.
In/for the audio-description, we annotated verbal clues about the missing visual content given by the audio-description's additional narrator \citep{haeusler2020speechanno}.
In conformity to the analyses performed in the studies using not-naturalistic stimuli, we employed a standard multi-level, voxel-wise general linear model (GLM) % in order to???
% Practical reasons = Es war viel einfacher nouns der audio-description als Frameinhalt des Films zu annotieren
For practical reasons, and encouraged by \citep{aziz2008modulation} and \citep{aminoff2013role}, we focus on the audio-description as a possible life-like stimulus free from any task to localize a ``visual area'' in individual study participants.

\section{Methods}
\todo[inline]{Specific data outputs should be explicitly referenced via data citation (see Data Records and Data Citations, below)}
\todo[inline]{MIH: we should consider making a statement how often these datasets have been analyzed be independent groups already -> Frage: ist die Liste auf psychoinformatics.de ist aktuell/erschöpfend? Ist dann schnell eingebaut}
\todo[inline]{entsprechend der neuen Infos hier, oben das Ende der Einleitung kürzen}
We used data from three publicly available datsets as part of the studyforrest dataset (\href{http://www.studyforrest.org}{studyforrest.org}) that has already been used by other research groups for independent research questions before. We used fMRI data from 14 subjects who took part in three different studies. Namely the same subjects were
a) listening to the audio-description (AO study) \citep{hanke2014audiomovie}) of the movie ``Forrest Gump'', a dataset already used by [XY].
b) watching the actual audio-visual movie (AV study) \citep{hanke2016simultaneous}, a dataset already used by [XY].
c) participating in a dedicated block-wise visual localizer (LOC study) \citep{sengupta2016extension}, a dataset aready used by [XY]. An exhaustive description of the participants, stimulus creation, procedure, stimulation setup, and fMRI acquisition can be found in the corresponding publications  \citep{hanke2014audiomovie, hanke2016simultaneous, sengupta2016extension}. Following is a brief summary of most important aspects.
\todo[inline]{Fokus des gesamten Methodenteils liegt auf den Naturalistic Stimuli; LOC study ist bisher effektiv nicht mit drin}

@@

\subsection{Stimulus Annotation}
\todo[inline]{einleitendes Blabla zu haeusler2020speechanno}
\todo[inline]{allg. überarbeiten; deutlich machen, WARUM WAS WIE annotiert wurde}
% Florian hat 2 Regeln falsch verstanden, sonst war übereinstimmung 90-95%
% Kategorie ``++'' enthält ausnahmesweise auch adverbiale Best. der Zeit.
% ggf. angeben, dass die effektiv identisch waren
\todo[inline]{aus Speech-Anno Paper 'descriptive-statistics-anno.py' übernehmen \& anpassen, um Statistiken und runcommand-file zu erstellen}
A further annotation of the audio-description's narrator was done manually: Two
persons performed a categorization of nouns embedded in sentences spoken by the
narrator to describe the movie's missing visual content.
Categories focus on the cinematographic scene's environment, inherent objects, persons, and a person's appearance (cf. table \ref{tab:descr-nouns})..
A categorizing of nouns that serve as auditory cues about the movie's visual content. Comprised categories focus on the cinematographic scene's environment (geo, geo-room; setting\_new, setting\_old), inherent persons (female, female name; male, male name, person), their appearance (face, head; body, bodypart), and objects (object, furniture).
The nouns are categorized by the clue they provide about a cinematographic scene's environment \todo{maybe skip the names and just cite the table} (geo, geo-room; setting\_new, setting\_rec), its inherent persons (female, female name; male, male name, person), a person's appearance (face, head; body, bodypart), and a scene's inherent objects (object, furniture).
A preliminary annotation according to the rules [entweder im laufenden Text oder in Tabelle], einer neuen Tabelle oder im laufenden Text was done by one person and corrected in several runs by the author.

@@

\subsection{Statistical analysis}
For both naturalistic stimli, we conducted a standard two-level general linear model (GLM) analysis in FEAT to create subject-specific results ($Z$-maps). A subsequent, third-level analysis averaged contrast estimates over subjects.

\subsubsection{first-level}
\paragraph{Regressors}
We used an annotation of movie cuts and depicted locations \citep{haeusler2016cutanno} and an annotation of speech \citep{haeusler2020speechanno} to create the FSL event files resp. regressors.
First, both annotations were split via \href{"https://github.com/chrhaeusler/studyforrest-data-annotations/blob/master/code/researchcut2segments.py"}{python script} into eight parts corresponding to the eight segments used as stimuli during fMRI scanning.
\todo[inline]{wenn ich folgend den "null regressor" nehme, darf ich den ganzen Run, glaube ich, in der 2nd level Analyse gar nicht benutzen??}
For the AO stimulus, we used the narrator's ``descriptive nouns'' (cf. table \ref{tab:descr-nouns}.
We created 11 regressors from the XY (selected?) original categories by joining / merging some categories (female, females, fname; male, males, mname; face, head) into one regressor (sex\_f; sex\_m; fahead).

\todo[inline]{cross reference to fig:reg-corr}

\begin{table*}[t]
    \caption{Overview of the events to build the 18 regressors for analysis of the AO stimulus. The first column contains the number of the regressor in the design file of FSL \citep{smith2004fsl}.
''fg\_ad\_lrdiff (left-right volume difference) and ``fg\_ad\_rms'' (root mean square loudness) represent low-level auditory nuissance regressors comprising one event for every movie frame (40ms).}
\label{tab:regressors}
\footnotesize
\begin{tabular}{lp{3.5cm}lllllllll}
\toprule
\textbf{label} &  \textbf{description} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} \\
\midrule
body & XYleft-right volume difference & rBodyAll & rBodyI & rBodyII & rBodyIII & rBodyIV & rBodyV & rBodyVI & rBodyVII & rBodyVIII \tabularnewline

fg\_ad\_lrdiff & left-right volume difference & rFgadlrdiffAll & rFgadlrdiffI & rFgadlrdiffII & rFgadlrdiffIII & rFgadlrdiffIV & rFgadlrdiffV & rFgadlrdiffVI & rFgadlrdiffVII & rFgadlrdiffVIII \tabularnewline
fg\_ad\_rms & root mean square & rFgadrmsAll & rFgadrmsI & rFgadrmsII & rFgadrmsIII & rFgadrmsIV & rFgadrmsV & rFgadrmsVI & rFgadrmsVII & rFgadrmsVIII \tabularnewline
\bottomrule
\end{tabular}
\end{table*}

% over length of each noun
The regressors were modeled as boxcar functions at the end of each noun with a duration of 200 ms.
If a segment did not contain a single event for a specific regressor, a null regressor was chosen for that segment.
Five regressors related to the cinematographic cuts (s. below) were added to built contrasts of cross-modal negative control.
Two regressors reflecting auditory (low-level) features (left-right loudness volume / amplitude??? difference; root mean squared amplitude) aligned to the frame rate of (40\,ms) were modeled to reduce nuisance effects.
An overview and short explanation of the 11 regressors and 5 + 2 additional nuisance regressors can be found in Table xy.
% entgegen der Masterarbeit kommen hier für den Film keine Abbildungen zur Verdeutlichung, weniger Text; no cut erkläre ich nicht lang & breit
% die regressoren settinge_new & setting_old aus dem Hörspiel habe ich meiner meinung nach unnötigerweise im Film mit-modelliert; lasse mich da aber auch umstimmen
% -> noch mal reingucken; kamen im Grunde nur "auditorische Areale" als Cluster vor; umgekehrt gab's bei der visuellen Regressoren im Hörbuch keine sign. Cluster
For the audio-visual stimulus, we categorized the depicted location in the frame following one of the 869 cuts in the movie to built five regressors: 1) unfamiliar setting (US), 2) familiar setting (FS), 3) locale switch (LS), 4) unfamiliar perspective (UP), 5) familiar perspective (FP).
In order to build negative control contrasts, a sixth regressors was created by pseudo-randomly choosing frames present within a shot and apart from a cut. Regressors were modeled as boxcar function lasting 200\,ms after a cut.
An overview and short explanation of the six regressors and the additional nuisance regressors reflecting (auditory and) visual low-level features can be found in Table xy.
For both stimuli, regressors were convolved with a double gamma canonical hemodynamic response function (HRF).
Their temporal derivatives were added to compensate for small timing differences \citep{friston1998event}.
Six motion parameters were used as additional nuisance regressors. Finally, designs were filtered with the same high-pass filter (cutoff period of 150\,s) as the BOLD time series.

@@

% From Poster:
% 1. PPA shows increased activation during non-visual, complex auditory stimulation that provides incidental spatial information.
% 2. only minor temporal correlation of regressors of the audio drama & movie that were not designed for experimental research.
% 3. but still, alternative contrasts show significant clusters in auditory cortices.
% 4. inter-individual differences: for two subjects, an alternative audio-contrast shows bilaterally significant clusters whereas the primary contrast shows no significant clusters.
% 5. audio drama shows bilaterally increased activation in subject 4 in which the visual localizer shows an unilateral cluster.
% 6. nevertheless, a  complex auditory stimulus might allow individual localization of a functionally defined brain region.
% 7. results of other studies suggest7 the PPA does not exclusively process the ``spatial layout''" but ``contextual associations''.
% 8. an audio drama might be suitable as ecologically more valid ``localizer'' for a variety of brain functions.

\section{Discussion (movie)}
lore ipsum
